We outline the outputs of the simulation here to facilitate the discussion
of the design of the priors used in the simulation. The simulation
provides PDF estimates for many of the output variables. Variables
of the most interest include the time dependence and $\alpha$, which is
defined to be the projection angle between the plane of the sky and the merger axis. Other output variables are dependent on $\alpha$ and the time
dependence. Specifically, the simulation denotes the time dependence by
providing several characteristic time-scales, including the time
elapsed between the collision and when the subclusters first reach apoapsis
($T$) and the time-since-collision.  

The two versions of the time-since-collision variables $TSC_0$ and
$TSC_1$ denotes different possible merger scenarios. 1) We call the scenario for which the subclusters are
moving apart after collision to be ``outgoing" and it corresponds to the
smaller $TSC_0$ value, and 2) we call the alternative scenario 
``incoming" for which the subclusters are approaching each other after turning
around from the apoapsis for the first time and it corresponds to $TSC_1$.
We describe how we use to break the degeneracies of the two scenarios in
section \ref{sec: positionprior}. 
 
The simulation also output estimates of variables that characterize
the dynamics of the merger. The 3D velocities, both at the time of the
collision ($v_{3D}(t_{col})$) and at the time of observation
($v_{3D}(t_{obs})$) are provided. The maximum 3D separation ($d_{max}$),
which is defined to be the distance between the position of collision to
the apoapsis, is also part of
the outputs. (See the lower half of Table \ref{tab:outputs} for all the outputs).
%Here we present results based on:\\  %1) a flat radio prior\\
%2) a uniform prior over a range of most likely 3D separations\\
%3) a Gaussian prior  
%We discuss in subsection \ref{sec:priors}  on the use of the default filters
%and two new filters designed according to the observed data and the physics of the radio relic.
%
%\textbf{While the underlying formalism of the Monte Carlo simulation is
%    based on the Bayes theorem, we caution the reader that this simulation
%    does not correspond to a conventional Bayesian parameter estimation but
%    more similar to the Bayesian uncertainty estimation method mentioned in Saltelli 
%    et al. (2004). (See appendix \ref{} for a more in-depth discussion)}

